Check experimental design

### 2021-10-15 analysis/01_experimental-design.Rmd
De-packagify the project
Included an index-coded design for computing contrasts

```{r check-design, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(here)

@@

```{r check-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
dummy_design <- as.data.frame(design)
for(i in 4:ncol(dummy_design)) {
  dummy_design[,i] <- as.factor(dummy_design[,i])
}

@@

>>>>

```{r load-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(fastDummies)
library(here)

@@

```{r dummy-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
dummy_design <- as.data.frame(design)
for(i in 4:ncol(dummy_design)) {
  dummy_design[,i] <- as.factor(dummy_design[,i])
}

@@

# Index-code the design

We also need to consider how we are computing contrasts to answer our specified hypotheses. To do so, we index-code where every attribute level is included such that every attribute is its own implied intercept. Note that for a non-Bayesian model, index coding in this way would not be identified. However, for a Bayesian model with proper priors, all parameters are identified. Additionally, the contrasts even of unidentified parameters are identified.

```{r index-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
index_design <- as.data.frame(design)
for(i in 4:ncol(index_design)) {
  index_design[,i] <- as.factor(index_design[,i])
}

# Rename the variables.
colnames(index_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get a index-coded version of all the attribute levels.
index_design <- dummy_cols(
  index_design, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the index variables.
colnames(index_design)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Save index-coded design output
write.csv(index_design, here("data", "derived_data", "index_design.csv"))
```
